Superabsorption of light by nanoparticles

### 2015-10-08 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/response-letter/response-letter.tex

\documentclass[a4paper]{article}
\usepackage{a4wide}
% \usepackage{graphicx}
% \usepackage{amssymb,amsmath}
% \usepackage{booktabs}
\usepackage[english]{babel}
% \usepackage{multirow}
\usepackage{graphicx}% Include figure files
% \usepackage{color}
\emergencystretch=35pt
\usepackage[pdftex,unicode,colorlinks, citecolor=blue,%
filecolor=black, linkcolor=blue, urlcolor=black]{hyperref}
\usepackage[figure,table]{hypcap}

\begin{document}
\begin{center}
  Response Letter
\end{center}
Dear Editor,
\vspace{10pt}

Many thanks for sending us referees’ reports on our manuscript
entitled ``Superabsorption of light by nanoparticles'' by K. Ladutenko
et al. (editorial code NR-COM-08-2015-005468). We are pleased with
overall very positive tone of these reports, as well as with referees’
constructive comments.

@@

We have addressed all the comments of the referees, and we present our
response and the summary of the changes made to the manuscript below.
\vspace{10pt}
\\
Sincerely Yours,\\
On behalf of the authors,\\
Konstantin Ladutenko

\vspace{10pt}

\newpage
\textbf{Reviewer \#1 comments}

\begin{tabular}[!H]{l|p{0.9\textwidth}}
\quad & 1. The authors claimed ``Combined effect of these resonances is
presented to produce the flat and relative broadband electric
resonance response.'' Nevertheless, the broadened absorption band is
not very broad. Is there any further way to predict a broadband light
absorption. For instance, a broadband absorption in the whole visible
spectral range. Maybe, a possible way of using the dispersed size
scale nanoparticles should be added for improving the study.
\end{tabular}\\

@@

\begin{figure}
  \includegraphics[width=0.35\textwidth]{overview-Qabs-a1}
   \includegraphics[width=0.60\textwidth]{overview-Qabs-all-a1}
  \caption{(a-c) Same as Fig.2 of the manuscript with different
    fitness function: the optimization aims to maximize the electric
    dipole absorption. (Missing points did not pass the stability
    test.) (d) $Q_{abs}$ for maximized $\tilde{a}_1$ from the first
    subplot of present figure without the additional stability test
    (green line) compared with $Q_{abs}$ optimization regarding all
    multipoles (black line, same as in Fig 2(a) of the
    manuscript).\label{fig:a1max}}
\end{figure}

\begin{tabular}[!H]{l|p{0.9\textwidth}}
\quad & 3.  In Fig. 3 (c), the authors observed a flat top of electric
dipole resonance. They attributed this flat resonance to the excited
several electric dipole resonances with close resonance
frequencies. Nevertheless, as we can see in Fig. 3 (d), even without
considering the resonances located in outer and inner shell, the
resonance inside the core is much broader than the other two
cases. The authors should explain this broadened resonance clearly.
\end{tabular}

We thank the referee for pointing this out, we must have not explained
this point clearly. The most interesting feature of this resonance
that we wanted to bring attention to is that the resonance has an
unusual flat top. The main shape and width of the resonance is
explained by one dominating dipole mode, as it is seen in the mode
decomposition in Fig.~3(d). Two additional electric dipole resonances
are much weaker, but their contribution "flattens" the top of the
combined absorption resonance. We have clarified this in the modified
manuscript changing the caption of Fig.~(3), after ``Panel~(d) shows
the superposition of the squared absolute values of the Mie
coefficients for electric dipole contribution inside each layer'' we
added ``of design from panel~(c), and it explains an almost
flat top of the electric dipole resonance.''

\begin{tabular}[!H]{l|p{0.9\textwidth}}
\quad & 4.  Some sentences are not clear to me. For instance, ``there
is a strong conterplay between the increased absorption for larger
particles vs size for smaller particles''.  In summary, I do not think
the manuscript is acceptable at its current stage.
\end{tabular}%

### 2015-10-08 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/2015-Ladutenko-Qabs.tex
Corrected quotes

The stochastic algorithm utilized in our approach is very generic and
the optimization can be repeated for any desired wavelength or
wavelength range.  As a result, one can design absorbers with broad
spectra or spectrally-selective absorbers with almost arbitrary
prescribed properties.  One can also achieve broadband performance by
mixing particles whose absorption is optimized for different
wavelengths. We have verified that due to the strong localization of
electric dipole field it is possible to design dimers whose absorbing
properties are dominated by the properties of individual particles,
and not by their mutual interaction. As a result, by appropriately
spacing the resonances of individual particles, their mixture will
exhibit a combined broadband response. Providing such an additional
control, this approach complements the case of self-organized
particles of various size and shape, which was experimentally proven
to have a wide absorption band~[ACS-AMI-Liu-2015]. % Reference to the
% paper mentioned with the reviewer in his second comment.
Further control of the absorption spectrum can be achieved by
arranging our spherical structures in a periodic and non-periodic
arrays.

>>>>

The stochastic algorithm utilized in our approach is very generic and
the optimization can be repeated for any desired wavelength or
wavelength range.  As a result, one can design absorbers with broad
spectra or spectrally-selective absorbers with almost arbitrary
prescribed properties.  One can also achieve broadband performance by
mixing particles whose absorption is optimized for different
wavelengths. We have verified that due to the strong localization of
electric dipole field it is possible to design dimers whose absorbing
properties are dominated by the properties of individual particles,
and not by their mutual interaction. As a result, by appropriately
spacing the resonances of individual particles, their mixture will
exhibit a combined broadband response. Providing such an additional
control, this approach complements the case of self-organized
particles of various size and shape, which was experimentally proven
to have a wide absorption band~\cite[ACS-AMI-Liu-2015]. % Reference to the
% paper mentioned with the reviewer in his second comment.
Further control of the absorption spectrum can be achieved by
arranging our spherical structures in a periodic and non-periodic
arrays.
